% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

%% 基本信息
\name{Li Boqian}
\basicInfo{
  \email{liboqian0543@outlook.com} \textperiodcentered\ 
  \phone{(+86)198-195-43890} \textperiodcentered\ 
  %% \faCalendar{Date of birth: Oct. 2000} \textperiodcentered\ 
  %%\faGroup {Gender: male} \
  }

%% 教育背景
\section{\faGraduationCap\  EDUCATION}
\datedsubsection{\textbf{Tiangong University}, Tianjin City,China}{Aug. 2019 -- Present}
\textit{Undergraduate.}\  Communication Engineering, expected to graduate in Jun. 2023. \\ 
\textbf{Grades} 
\begin{itemize}
    \item \textit{GPA:}\ 3.11 (4.0 total)
    \item \textit{Major courses: }\ embedded system (95), signal and system (86), communication principle (72), control theory (78), data communication (82).
    \item \textit{Additional courses:}\ mathematical modeling, machine learning and big data processing.
    \item \textit{English level:}\ Pass CET-6.
\end{itemize}

%% 科研经历
\section{\faFlask\ SCIENTIFIC RESEARCH}
\datedsubsection{\textbf{Fundus image mosaic}}{Jun. 2021 - Sept. 2021}
Participate in graduate laboratory projects, medical image processing
\begin{itemize}
  \item Use a machine learning algorithm to create a fundus image mosaic and synthesize local fundus images from multiple angles into a panoramic image.
\end{itemize}
 
\datedsubsection{\textbf{Heart rate and blood pressure measurement method based on TOI}}{Sept. 2021 - Present}
Graduation design, physiological information collection
\begin{itemize}
  \item I utilized a camera to record a facial video, developed a video processing algorithm on MATLAB, and successfully extracted heart rate and blood pressure information from the video.
  \item To enhance the precision and accuracy of this method based on Transmittance Optical Imaging (TOI), I conducted a thorough study on the factors that affect these measurements, including various environmental and physiological factors.
  \item Moreover, I implemented machine learning algorithms to further improve the accuracy of the heart rate and blood pressure measurements.
\end{itemize}
 

%% 学生工作
\section{\faBriefcase\ STUDENT WORK}
\datedsubsection{\textbf{The Student Union}\ Officer}{Sept. 2019 - Sept. 2020}
 
    \begin{itemize}
      \item I am responsible for managing the official account of the School of International Education at Tianjin University of Technology. My duties include writing documents, taking photos of events, and editing videos.
      \item Work with foreign students and have participated in English translation.
    \end{itemize}
     
\datedsubsection{\textbf{Class cadre}\ Publicity committee member}{Sept. 2019 - Sept. 2021}
\datedsubsection{\textbf{Class cadre}\ League branch secretary}{Sept. 2021 - Present}

\section{\faFlag\ HOBBY}
\begin{itemize}[parsep=0.5ex]
  \item I love acting. I'm a member of the college choir and have participated in school and municipal chorus competitions. I've also been a program host and taken part in speech and recitation competitions, achieving excellent results.
  \item Electronic enthusiasts, with work experience in open source projects.
\end{itemize}



%% 自我评价
\section{\faInfo\ SELF-EVALUATION}
\large I enjoy tackling new challenges and helping others with a positive service attitude, excellent communication and teamwork skills. I'm passionate about learning and keeping up with new technologies. I'm a responsible and confident self-starter, with strong analytical and problem-solving abilities, able to adapt to changing situations.
 
\newpage 
\begin{center}
\LARGE APPENDIX
\end{center}


\section{\faCheck\ PROJECT}
\datedsubsection{\textbf{Infusion alarm device based on 51 microcontroller}}{Dec. 2019 - Mar. 2020}
Competition project, embedded development
\begin{itemize}
  \item The photoelectric sensor measures the infusion state. An alarm will sound when the liquid in the infusion tube has finished flowing.
  \item Judge the liquid flow rate and adjust the closing degree of the infusion valve via the steering gear, based on the speed set by the user.
\end{itemize}
 
\datedsubsection{\textbf{Autonomous vehicle}}{Oct. 2020 - Jan. 2021}
Participate in graduate laboratory projects, embedded development
\begin{itemize}
  \item The hardware control module is designed to communicate with the core module and execute corresponding control commands.
  \item Control of lighting system, steering system and driving system.
\end{itemize}
 
\datedsubsection{\textbf{Remote amplitude frequency characteristic test device}}{Jul. 2021 - Oct. 2021}
Competition items, embedded development, digital signal processing
\begin{itemize}
  \item Use stm32f4 series microcontroller and DDS module to realize frequency sweep of components to be tested.
  \item Measure the corresponding amplitude and frequency characteristics through AD module.
  \item Send the data to the receiver and draw the amplitude-frequency characteristic curve image.
\end{itemize}
 
\datedsubsection{\textbf{Design of smart home system based on raspberrypi}}{Oct. 2021 - Oct. 2022}
Personal projects, embedded development, Internet development
\begin{itemize}
  \item The web front-end is designed based on Linux as the primary interactive interface for smart homes. It is used to monitor the running status of various devices and control them.
  \item Write back-end programs using Python and C to control TVs, lamps, air conditioners, and other equipment with Raspberry Pi.
\end{itemize}
 


\section{\faFile\ INTERSHIP}
\datedsubsection{\textbf{Huawei Co., Ltd}}{Aug. 2020 - Sept. 2020}
Learn about web development based on java and php
\begin{itemize}
  \item Server operation and maintenance
  \item WeChat official account background maintenance
\end{itemize}
 

\section{\faCogs\ PROFESSIONAL SKILLS}
\begin{itemize}[parsep=0.5ex]
  \item Programming languages: c, python, matlab
  \item Platform: embedded development, machine learning
\end{itemize}

% %% 所获荣誉
% \section{\faHeartO\ HONORS}
% % \datedsubsection{\textbf{优秀共青团员}}{2019 年12 月}
% % \datedsubsection{\textbf{优秀班干部}}{2020 年12 月}
% \datedsubsection{\textbf{创新杯竞赛（校级）}\ Third Prize}{Mar. 2020}
% \datedsubsection{\textbf{师生朗诵比赛（天津市市级）}\ Second Prize}{Aug. 2020}
% \datedsubsection{\textbf{节能减排竞赛（天津市市级）}\ Third Prize}{May. 2021}
% \datedsubsection{\textbf{新工科竞赛（天津市市级）}\ Third Prize}{Dec. 2021}

\section{\faFlickr\ OTHERS}
 
    \begin{itemize}
      \item \faGithub{\href{https://github.com/aurora0543}{ Personal homepage:https://github.com/aurora0543}}
    \end{itemize}
     

\end{document}